---
title: "Know about philosophy from different school"
output: html_document
---
#### This report is a guidebook with selected Q&A aims at finding out what kind of topics do philosophers from different school focus on.

 
#### The whole dataset :the dataset for the Philosophy Data Project contains over 300,000 sentences from over 50 texts spanning 10 major schools of philosophy. You can read more about the project on http://www.philosophydata.com/. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE,echo=FALSE}
packages.used=c("tm", "wordcloud", "RColorBrewer", 
                "dplyr", "tidytext")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library(tm)
library(wordcloud)
library(RColorBrewer)
library(dplyr)
library(tidytext)
source("../lib/plotfigure.R")
```

This report is prepared with the following environmental settings.

```{r}
print(R.version)
```

```{r read data, warning=FALSE, message=FALSE,echo=FALSE}
ps.data<-read.csv('../data/philosophy_data.csv',stringsAsFactors = FALSE)

```

## Question 1: Which schools are we going to explore?what does each school consist of?

For me,I am a totally beginner for philosophy and philosophors,especially considering the fact that I am an international student.Although I know about the famous philosophors like plato and aristotle,yet it is important to explore their philosophy from the perspective of schools. 

```{r explore data, warning=FALSE, message=FALSE}
#what are the schools in this dataset
ps.schools = unlist(unique(ps.data$school))
#what are the titles in this dataset
ps.titles =unlist(unique(ps.data$title))

ps.school.split = split(ps.data,ps.data$school)
ps.school.table = as.data.frame(table(ps.data$school))
colnames(ps.school.table)=c("school","count")
ps.school.table = ps.school.table[order(ps.school.table$count,decreasing =  TRUE),]
barplot(ps.school.table$count, las = 2, names.arg = ps.school.table$school,
        col ="lightblue", main ="Most frequent schools",
        ylab = "Sentence Count")
```



## Question 2: How philosophors  think about the world in general?

Firstly,we can see how philosophers think about the world by analyzing the frequency of certain words appearing in the sentences。

```{r data preprocessing,warning=FALSE, message=FALSE}
#Since the data has been lower-cased and tokenized,we can use the tokenized texts and remove all 
ps.corpus = Corpus(VectorSource(ps.data$tokenized_txt))
ps.corpus = tm_map(ps.corpus, removeNumbers)
ps.corpus = tm_map(ps.corpus, removePunctuation)
ps.corpus = tm_map(ps.corpus, removeWords, c("the", "and","also","two", "one","can","may","will","must","might","just","thus","therefore",stopwords("english")))
ps.corpus =  tm_map(ps.corpus, stripWhitespace)
```

```{r word-frequency}
ps.tdm.all<-TermDocumentMatrix(ps.corpus)
ps.tdm.tidy=tidy(ps.tdm.all)
ps.tdm.overall=summarise(group_by(ps.tdm.tidy, term), sum(count))
#word frequency 
ps.wordfreq <- data.frame(word =ps.tdm.overall$term ,freq=ps.tdm.overall$`sum(count)`)
ps.wordfreq <- ps.wordfreq[order(ps.wordfreq$freq,decreasing = TRUE),]
head(ps.wordfreq,20)
```
```{r, warning=FALSE, message=FALSE}
barplot(ps.wordfreq[1:20,]$freq, las = 2, names.arg = ps.wordfreq[1:20,]$word,
        col ="lightblue", main ="Most frequent words",
        ylab = "Word frequencies")
```

```{r, warning=FALSE, message=FALSE}
#wordcloud in general
wordcloud(ps.tdm.overall$term, ps.tdm.overall$`sum(count)`,
          scale=c(3,0.5),
          max.words=100,
          min.freq=100,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(8,"Dark2"))
```


We can see various philosophy topics in the high frequency words:
"things"and "man","world"、"nature"、"object"、"subject"and so on;
As we would like to identify interesting words for each sentence, we use [TF-IDF]to weigh each term within each sentence. It highlights terms that are more specific for a particular sentence. 

```{r,warning=FALSE, message=FALSE}
# compute TF-IDF weighted document-term matrices for individual sentences
ps.dtm <- DocumentTermMatrix(ps.corpus,
                          control = list(weighting = weightTfIdf,stopwords = TRUE))
#ps.dtm=tidy(dtm)
ps.dtm = removeSparseTerms(ps.dtm , 0.99)
freq = data.frame(sort(colSums(as.matrix(ps.dtm)), decreasing=TRUE))
wordcloud(rownames(freq), freq[,1], max.words=100, colors=brewer.pal(5, "Dark2"))
```

For each sentence,the "nature""existence""object" outstands,we can see that philosophers focus a lot on conceptual and abstract topics,which make them think about the essence of world and man.

## Question 3:How do philosophors from different school think about the world?What are the difference



#### For school analytic:
```{r,warning=FALSE, message=FALSE}
creat.wordcloud(ps.school.split[1],ps.data,names(ps.school.split[1]))
```

For school analytic:"theory","sense","truth","sense","fact" are the keywords

#### For school aristotle:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[2],ps.data,names(ps.school.split[2]))
```

For school aristotle:"will","must","reason","nature","animal" are the keywords

#### For school capitalism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[3],ps.data,names(ps.school.split[3]))
```

For school capitalism: Price,money ,capital are the main topics

#### For school communism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[4],ps.data,names(ps.school.split[4]))
```

For school communism: labour,value, production,capital are the main topics

#### For school continental:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[5],ps.data,names(ps.school.split[5]))
```

For school continental:"madness","form","relationship" appear the most

#### For school empiricism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[6],ps.data,names(ps.school.split[6]))
```

For school empiricism: "ideas/idea","reason" appear  frequently

#### For school feminism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[7],ps.data,names(ps.school.split[7]))
```

For school feminism:without doubt,"women/woman"appear most,"man","love","children" appear frequently

#### For school german_idealism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[8],ps.data,names(ps.school.split[8]))
```

For school german_idealism:quite abstract and conceptual words like "consciousness","self" and "law"

#### For school nietzsche:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[9],ps.data,names(ps.school.split[9]))
```

For school nietzsche:"life""virtue""god""love""soul"

#### For school phenomenology:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[10],ps.data,names(ps.school.split[10]))
```


For school phenomenology:"knowledge""experience""conciousness"

#### For school plato:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[11],ps.data,names(ps.school.split[11]))
```


For school plato:it is interesting "socrates" appears a lot of time

#### For school rationalism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[12],ps.data,names(ps.school.split[12]))
```

For school rationalism:Why "god" appear most here?Maybe it is always used as  counterexamples

#### For school stoicism:
```{r,warning=FALSE, message=FALSE,echo=FALSE}
creat.wordcloud(ps.school.split[13],ps.data,names(ps.school.split[13]))
```

For school stoicism:you can guess this school is from old greek period from the words"thou""thyself""thee"

## Conclusions
1. Philosophy focus mainly on conceptual and abstract topics

2. Different school of philosophers have their own topic
